DeepFovea++: Reconstruction and Super-Resolution for Natural Foveated Rendered Videos

### 2020-07-20 DeepFovea++ paper/paper.tex
Add changed paper

	\begin{multline} \label{eq:loss}
		\mathcal{L}=w_{\text{sv}}\,\mathcal{L}_{\text{sv}} + w_{\text{flow}}\,\mathcal{L}_{\text{flow}} + w_{\text{adv}}\,\mathcal{L}_{\text{adv}} + w_{\text{adv fft}}\,\mathcal{L}_{\text{adv fft}}\\
		+ w_{\text{flow}}\,\mathcal{L}_{\text{flow}} + w_{\text{LPIPS}}\,\mathcal{L}_{\text{LPIPS}}    
	\end{multline}

>>>>

\begin{multline} \label{eq:loss}
    \mathcal{L}=w_{\text{sv}}\,\mathcal{L}_{\text{sv}} + w_{\text{adv}}\,\mathcal{L}_{\text{adv}} + w_{\text{adv fft}}\,\mathcal{L}_{\text{adv fft}}\\
    + w_{\text{flow}}\,\mathcal{L}_{\text{flow}} + w_{\text{LPIPS}}\,\mathcal{L}_{\text{LPIPS}}    
\end{multline}
